DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-09-30 paper/background.tex
background revision (WIP)

\subsection{Deep End-to-End Control}
End-to-end training of deep neural network models is an active
research area in the fields of AI~\cite{Levine2016}.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/endtoend}
  \caption{Standard robotics control vs. DNN based end-to-end
    control. \fixme{figure must be redrawn}}
\end{figure}

- explosion of AI
- in particular, application of DNN in perception and control of robotics systems.
- end-to-end control is a promising technique.
  levine's publications?
- examples: nvidia's DAVE-II prototype, forest navigating drone
challenge problem: computing at low cost?

>>>>

In this section, we provide background on the application of deep
learning in robotics, particulary autonomous vehicles.

\subsection{Deep End-to-End Learning in Autonomous Vehicles}

%% - explosion of AI
%% - in particular, application of DNN in perception and control of robotics systems.
%% - end-to-end control is a promising technique.
%%   levine's publications?
%% - examples: nvidia's DAVE-II prototype, forest navigating drone
%% challenge problem: computing at low cost?

To solve the problem of autonomous driving, a standard approach has
been decomposing the problem into multiple sub-problems,
such as lane marking detection, path planning, and low-level
control, which together form a processing pipeline~\cite{Bojarski2016}.
Recently, researchers are exploring another approach that dramatically
simplifies the standard control pipeline by applying deep neural
networks to directly produce control outputs from senor
inputs~\cite{Levine2016}}. Figure~\ref{fig:end-to-end-control}
shows the differences between two two approaches.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/endtoend}
  \caption{Standard robotics control vs. DNN based end-to-end
    control. \fixme{figure must be redrawn}}
  \label{fig:end-to-end-control}
\end{figure}

The use of neural networks for end-to-end control of autonomous
driving was first demonstrated in late 1980s~\cite{Pomerleau1989}, but
its success has been limited at the time as its performance was not
sufficient enough.

%% \cite{Levine2016}: ``In this paper, we aim to answer
%% the following question: does training the perception and control systems jointly end-toend
%% provide better performance than training each component separately?''

%% \cite{Bojarski2016} nvidia paper
%% ``We trained a convolutional neural network (CNN) to map raw pixels from
%% a sin- gle front-facing camera directly to steering commands.''

%% ``Compared to explicit decomposition of the problem, such as lane
%% marking detec- tion, path planning, and control, our end-to-end system
%% optimizes all processing steps simultaneously. We''
